Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
comment on the primary stage

>>>>

\vl{The argument behind not training a deep convolutional network is a strawman argument.
There is a also learning stage inherent to our approach: LDA or LMNN. @writing}

\vl{I do believe that time-frequency scattering (or one of its variants, see McDermott or Patil or Sch\"{a}dler)
is, in a very precise way, mandatory to model the central auditory system. It's OK to think otherwise but that
should be motivated. @writing}
